\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.82,top=1.4cm,bottom=1.8cm]{geometry}
% Disable microtype font expansion (moderncv loads microtype; fontawesome5's
% bitmap shapes are not scalable, so auto-expansion crashes pdflatex).
\microtypesetup{expansion=false}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{etoolbox}
\usepackage{needspace}

% --- Visual palette: ink near-black for structure, navy for accents, ---
% --- sky for soft highlights, slate for body, softgray for descriptions.
\definecolor{ink}{HTML}{0B1220}
\definecolor{navy}{HTML}{1D4ED8}
\definecolor{azure}{HTML}{2563EB}
\definecolor{sky}{HTML}{60A5FA}
\definecolor{slate}{HTML}{334155}
\definecolor{softgray}{HTML}{6B7280}
\definecolor{deepgray}{HTML}{374151}
\definecolor{whisper}{HTML}{EFF6FF}
\definecolor{mist}{HTML}{F1F5F9}

% Override moderncv's internal palette (color1 drives section rules + headings,
% color2 is the name). Gives Experience/Projects headings a navy rule automatically.
\colorlet{color1}{navy}
\colorlet{color2}{ink}

% Body typography: name in ink, role in navy italic, sections in ink bold with
% the navy rule coming from moderncv classic itself.
\renewcommand*{\namefont}{\fontsize{28}{32}\bfseries\upshape\color{ink}}
\renewcommand*{\titlefont}{\fontsize{14}{16}\mdseries\slshape\color{navy}}
\renewcommand*{\addressfont}{\small\mdseries\slshape\color{softgray}}
\renewcommand*{\quotefont}{\large\slshape\color{slate}}
\renewcommand*{\sectionfont}{\Large\bfseries\color{ink}}
\renewcommand*{\subsectionfont}{\large\mdseries\slshape\color{navy}}

\setlength{\footskip}{45pt}

% --- Custom helpers ---------------------------------------------------------
% Body description under each bullet: slightly warmer than before.
\newcommand{\impact}[1]{{\color{slate}\small #1}}
% Metric: navy bold + a soft whisper background so the number pops.
\newcommand{\metric}[1]{%
  \begingroup
  \setlength{\fboxsep}{2pt}%
  \colorbox{whisper}{\color{navy}\bfseries\strut #1}%
  \endgroup
}
% Stakeholder chip: bracketed, sky italic, slightly stronger than before.
\newcommand{\stakeholders}[1]{{\color{azure}\footnotesize\textsf{\textit{[#1]}}}}
% Role label inside bullets (the bold lead-in): navy bold.
\newcommand{\rolebold}[1]{{\color{navy}\bfseries #1}}
% Callout box for Profile and project human/technical pairs.
\newcommand{\callout}[1]{%
  \begingroup
  \setlength{\fboxsep}{0.8em}%
  \noindent\fcolorbox{sky!40}{whisper}{%
    \begin{minipage}{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}%
      \color{slate}\small #1%
    \end{minipage}%
  }%
  \endgroup
}
% Visual separator: a softer, two-tone rule (navy dot + grey line).
\newcommand{\softrule}{%
  \vspace{0.45em}
  \noindent\hspace{0pt}{\color{navy}\rule{6pt}{2pt}}{\color{softgray!40}\rule[0.5pt]{0.92\linewidth}{0.4pt}}\hspace{0pt}%
  \vspace{0.35em}
}

% --- Identity ---------------------------------------------------------------
\name{Pedro Luis}{Lobato Barros}
\title{SRE \& Core Logic Lead}
\address{Bogotá D.C., Colombia}{Remote-first}{}
\phone[mobile]{+57~318~507~9105}
\email{pedro.lobato2610@gmail.com}
\social[linkedin]{lobaton2610}
\social[github]{Lob26}

\begin{document}
\makecvtitle
\vspace{-1.2em}

% --- Profile ----------------------------------------------------------------
\section{Profile}
\cvitem{}{%
  Software engineer with nearly two years in high-growth Fintech and Proptech. Track record of cutting operational wait times by up to \textbf{90\%}, defending production under live attack, and bridging backend systems (Python, Go, Ruby) with CRM ecosystems (Salesforce). Fluent across English and Spanish with Legal, Commercial and Operations.
}

\softrule

% --- Business capabilities --------------------------------------------------
% Clean 2x2 grid. Label lives on its own line so narrow columns don't hyphenate
% mid-word; descriptions kept short (~14 words) so each cell stays two lines.
\section{Business Capabilities}
\cvdoubleitem%
  {\faHandshake}{\rolebold{Stakeholder Management}\newline%
    \impact{Turn Legal, Commercial and Operations needs into engineering that ships.}}%
  {\faUsers}{\rolebold{Cross-functional Leadership}\newline%
    \impact{Bridge engineering, product and business so decisions land, not stall.}}
\cvdoubleitem%
  {\faShieldVirus}{\rolebold{Technical Ownership}\newline%
    \impact{End-to-end ownership of core engines, architecture through post-incident review.}}%
  {\faBell}{\rolebold{Incident Response}\newline%
    \impact{Calm, visible post-mortems --- people see what happened and what changed.}}

\softrule

% --- Technical toolbox (clean single-column list, left label / right content)
\section{Technical Toolbox}
\cvitem{Languages}{Python, Go, Ruby, TypeScript, Solidity, JavaScript, SQL}
\cvitem{Integrations}{Salesforce, Slack, RabbitMQ, REST APIs, custom AWS \& Slack wrappers}
\cvitem{Databases}{PostgreSQL, MySQL}
\cvitem{DevOps \& Cloud}{AWS, GCP, Docker, CI/CD, GitHub Actions}
\cvitem{Practices}{SRE principles, security architecture, system design, code review}
\cvitem{Languages spoken}{English (C1) · Spanish (Native)}

\softrule

% --- Experience -------------------------------------------------------------
% Keep the heading with the first entry so it does not float at a page bottom.
\needspace{10\baselineskip}
\section{Experience}
\nopagebreak

\cventry{Aug 2024 -- Present}%
  {\textbf{Software Engineer} --- SRE \& Core Logic Lead}%
  {Duppla}%
  {Bogotá, Colombia}%
  {\textit{Technical ownership · Cross-functional lead}}{%
  I own the core business engines and the reliability practice, acting as a translator between engineering and the commercial, legal and operations teams.
  \begin{itemize}
    \item \rolebold{Core Product Ownership} \metric{(--83\%)} \stakeholders{Commercial · Operations}\\
      \impact{Partnered with Operations and Commercial to redesign the Real Estate Evaluator. A 90-minute wait collapsed to 15 --- the 83\% returned most of an afternoon to analysts talking to clients instead of refreshing a screen.}
    \item \rolebold{Live Attack Defense} \metric{(100\% repelled)} \stakeholders{Engineering · Leadership}\\
      \impact{A bot slipped in a crafted request that exposed the full API surface; attacks on billing and reporting endpoints followed within minutes. I caught the attack live through the observability I had designed, shipped defenses on the targeted endpoints in real time, and hardened the backend into a posture that has repelled every subsequent attempt.}
    \item \rolebold{Contract Automation} \stakeholders{Legal · Product}\\
      \impact{Leading a contract generation engine co-designed with Legal, unblocking deal flow during Series A preparation.}
    \item \rolebold{Salesforce Integration} \stakeholders{Commercial · RevOps}\\
      \impact{Bridge engineer between backend services and the commercial platform, giving the revenue team a CRM source of truth.}
    \item \rolebold{Developer Experience} \metric{(--30\%)} \stakeholders{Engineering}\\
      \impact{Custom AWS and Slack wrappers that standardised tooling and removed 30\% of technical debt --- new engineers ship on day one instead of deciphering.}
  \end{itemize}
}

\cventry{Jun 2024 -- Aug 2024}%
  {\textbf{Software Development Intern}}%
  {Duppla}%
  {Bogotá, Colombia}%
  {\textit{First production ownership}}{%
  Took the early leap from academic code into production work: backend services for customer assessment and internal logistics on Slack.
  \begin{itemize}
    \item \rolebold{Business Process Migration} \metric{(--90\%)} \stakeholders{Legal · Risk · Origination}\\
      \impact{Rebuilt the Client Evaluator backend in conversation with Legal, Risk and Origination. Thirty minutes of manual work collapsed into three --- 90\% of queue time returned to the people who actually weigh the hard cases.}
    \item \rolebold{Internal Logistics} \stakeholders{People Ops}\\
      \impact{Slack automation for attendance and office logistics still used daily by HQ.}
    \item \rolebold{Stability} \stakeholders{IT}\\
      \impact{Credentialing code running with minimal maintenance two years post-launch --- the quiet kind of reliability.}
  \end{itemize}
}

\softrule

% --- Education --------------------------------------------------------------
\section{Education}
\cventry{2020 -- 2027 (Expected)}%
  {\textbf{B.S. Systems \& Computing Engineering}}%
  {Universidad de los Andes}%
  {Bogotá, Colombia}%
  {}{%
    \impact{Relevant coursework: Software Architecture, Distributed Systems, Cybersecurity, Databases, Cloud Computing.}%
  }

\newpage

% --- Notable Projects -------------------------------------------------------
\section{Notable Engineering Projects}

% A project card: title (+ optional metric right-aligned), stakeholders line,
% human problem paragraph, technical answer paragraph. Uses the full main
% column (empty label slot) so the title and metric pill share one line.
\newcommand{\projectcard}[5]{%
  % #1 title  #2 metric (may be empty)  #3 stakeholders  #4 human problem  #5 technical answer
  % Parbox lets us use \par inside \cvitem's content cell (moderncv disallows it otherwise).
  \cvitem{}{%
    \parbox{\linewidth}{%
      {\color{ink}\bfseries #1}\ifstrempty{#2}{}{\hfill\metric{#2}}\\[2pt]%
      \stakeholders{#3}\\[3pt]%
      {\color{slate}\small\textbf{Human problem.}~#4}\\[1pt]%
      {\color{slate}\small\textbf{Technical answer.}~#5}%
    }%
  }%
  \vspace{0.35em}%
}

\projectcard%
  {Real Estate Evaluation Engine}%
  {-83\% processing time}%
  {Commercial · Operations}%
  {Commercial analysts waited 90 minutes per property evaluation --- long enough for a client to cool off and a negotiation to stall.}%
  {Migrated the engine out of Retool into a custom intranet, tightened pricing logic and automated upstream data flows so analysts see a result in 15 minutes.}

\projectcard%
  {Business Client Evaluator}%
  {-90\% cycle time}%
  {Commercial · Origination}%
  {Origination sat on every prospect for 30 minutes of manual screening --- good leads went cold in the queue while unfit ones ate the same half-hour before they could be discarded.}%
  {Full backend rewrite: new data model, leaner queries and asynchronous scoring. Evaluation cycle dropped from 30 minutes to 3, letting the team act on signal instead of grinding through noise.}

\projectcard%
  {Contract Automation Engine}%
  {}%
  {Legal · Product}%
  {Every contract was hand-crafted from manual templates riddled with typo-prone patterns and incomplete variable slots. The team burned hours per deal, lost traceability between versions, and shipped errors that slipped past review.}%
  {Rebuilt the templates from scratch to remove error-prone variable patterns, then wired a generation-and-review pipeline that pulls each business opportunity's data automatically --- every contract is now versioned, validated, and auditable end-to-end.}

\projectcard%
  {Live Attack Defense}%
  {100\% repelled}%
  {Engineering · Leadership}%
  {A bot slipped in a crafted request that revealed our full API surface; within minutes, attacks flooded the billing and reporting endpoints --- the kind of hit that moves real money.}%
  {Caught the attack live through the observability I had designed, shipped endpoint-level defenses on the targeted routes before they could execute, and hardened the backend into a posture that has repelled every subsequent attempt as attack volume has grown.}

\cvitem{\textbf{Public Repositories}}{%
  \href{https://github.com/Lob26/ISIS2603_CulturasGastronomicas_Back}{\faGithub\ Fullstack Spring/Angular App}%
  \hspace{1em}\textcolor{softgray}{\textbar}\hspace{1em}%
  \href{https://github.com/Lob26/ISIS2304_Alohandes}{\faGithub\ JDO Data Persistence Project}%
}

\end{document}
